Cores from kicks: constraints for observations of gravitational recoil in elliptical galaxies

### 2024-05-14 papers/paper-corekick/paper-corekick.tex
Minor comments and thoughts

\subsection{Mass density profiles in three dimensions}
\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{density_3d}
    \caption{
        Three dimensional stellar mass density, with the line colour corresponding to the kick velocity of the SMBH. 
        All simulations with $\vk \geq 0.5v_\mathrm{esc}=900\,\kmps$ share the same colour, as there is little variation in the profiles for these kick velocities. 
        A clear dichotomy is revealed in the mass profiles, whereby high kick velocities induce a core, and low kick velocities do not, with a sudden transition at $\vk=540\,\kmps$.
        }
    \label{fig:density3d}
\end{figure}
Before considering the projected, 2D stellar mass density profiles of the merger remnants, we investigate the 3D stellar mass distribution.
This alleviates the influence of projection effects on inferring if a core has formed during the BH binary merger process, and gives insight into the dependence of how matter is spatially distributed as a function of the recoiling SMBH kick velocity.
For the $\vk=0\,\kmps$ case, we determine the SMBH influence radius to be $r_\mathrm{infl}\simeq 1.5\,\mathrm{kpc}$, and is insensitive to the time of measurement.
In \autoref{fig:density3d}, we observe a clear dichotomy in the 3D spatial distribution of stellar mass, with mergers that had an SMBH with a kick velocity $\vk<540\,\kmps$ having more mass in the central $3\,\mathrm{kpc}$ ($2r_\mathrm{infl}$) than those mergers with $\vk>540\,\kmps$. 
All merger remnants have a consistent mass density distribution at $r>3\,\mathrm{kpc}$. 
Additionally, for kick velocities $\vk<540\,\kmps$, we observe a gradient in decreasing central stellar density with increasing kick velocity.
We check the time dependence of this dichotomy by constructing the 3D stellar mass distributions at additional times $t=0.056\,\mathrm{Gyr}$, $t=0.094\,\mathrm{Gyr}$, and $t=0.12\,\mathrm{Gyr}$, and find the dichotomy persists, with the same kick velocity split.

@@

    Some incongruencies:
    \begin{itemize}
        \item In 3D density, there is a smooth decrease with increasing kick velocity, until it saturates. How do we then explain a peak in the core radius in the projected density maps?
    \end{itemize}
}

>>>>

\subsection{Mass density profiles in three dimensions}
\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{density_3d}
    \caption{
        Three dimensional stellar mass density, with the line colour corresponding to the kick velocity of the SMBH. 
        All simulations with $\vk \geq 0.5v_\mathrm{esc}=900\,\kmps$ share the same colour, as there is little variation in the profiles for these kick velocities. 
        A clear dichotomy is revealed in the mass profiles, whereby high kick velocities induce a core, and low kick velocities do not, with a sudden transition at $\vk=540\,\kmps$.
        }
    \label{fig:density3d}
\end{figure}
Before considering the projected, 2D stellar mass density profiles of the merger remnants, we investigate the 3D stellar mass distribution.
This alleviates the influence of projection effects on inferring if a core has formed during the BH binary merger process, and gives insight into the dependence of how matter is spatially distributed as a function of the recoiling SMBH kick velocity.
\drafting{Maybe move the following two sentences to Atte's section
To centre the data herein, we use the shrinking sphere method \citep{power2003} to determine the stellar centre of mass, and find the time evolution of the CoM does not systematically vary with kick velocity.
Consequently, we are confident that our results are not a result of malign centring.}
For the $\vk=0\,\kmps$ case, we determine the SMBH influence radius to be $r_\mathrm{infl}\simeq 1.5\,\mathrm{kpc}$, and is insensitive to the time of measurement.
In \autoref{fig:density3d}, we observe a clear dichotomy in the 3D spatial distribution of stellar mass, with mergers that had an SMBH with a kick velocity $\vk<540\,\kmps$ having more mass in the central $3\,\mathrm{kpc}$ ($2r_\mathrm{infl}$) than those mergers with $\vk>540\,\kmps$. 
All merger remnants have a consistent mass density distribution at $r>3\,\mathrm{kpc}$. 
Additionally, for kick velocities $\vk<540\,\kmps$, we observe a gradient in decreasing central stellar density with increasing kick velocity.
We check the time dependence of this dichotomy by constructing the 3D stellar mass distributions at additional times $t=0.056\,\mathrm{Gyr}$, $t=0.094\,\mathrm{Gyr}$, and $t=0.12\,\mathrm{Gyr}$, and find the dichotomy persists, with the same kick velocity split.

@@

    Some incongruencies:
    \begin{itemize}
        \item In 3D density, there is a smooth decrease with increasing kick velocity, until it saturates. How do we then explain a peak in the core radius in the projected density maps?
    \end{itemize}

    For simulation with vk 480 and less, the BH and the CoM coincide (on approx. scales). 
    Keplerian orbits only present in those sims where the BH and CoM are close (also confirmed with early analysis of snapshot 8 instead of 16) and also where the BH velocity is less than 300km per s.

    We can use results from this work to identify systems where the SMBH is settling, difficult (impossible?) to determine exact history of system once BH settled. 
}
